Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-02-12 tex/test-WW-type-00s-PS.tex
TEX
alexei

\preprint{JLAB-THY-17-XXXX}

@@

\author[a]{S.~Bastami}
%\author[b]{M.~D.~Albright}
\author[c]{H.~Avakian}
\author[d]{A.~V.~Efremov} 
\author[e]{A.~Kotzinian} 
\author[f]{B.~U.~Musch} 
\author[e]{B.~Parsamyan} 
\author[b,c]{A.~Prokudin} 
\author[g]{M.~Schlegel} 
\author[a,g]{P.~Schweitzer} 
\author[g]{W.~Vogelsang}

\affiliation[a]{Department of Physics, University of Connecticut, 
	Storrs, CT 06269, U.S.A.}
\affiliation[b]{Division of Science, Penn State Berks, Reading, 
	PA 19610, USA}
\affiliation[c]{Thomas Jefferson National Accelerator Facility, 
	Newport News, VA 23606, U.S.A.}
\affiliation[d]{Joint Institute for Nuclear Research, Dubna, 
	141980 Russia}
\affiliation[e]{Dipartimento di fisica teorica, Universit\`a degli 
   studi di Torino, and Sezione dell'INFN di Torino, Via Pietro Giuria 1, 
   10125 Torino, Italy}
\affiliation[f]{Institut f\"ur Theoretische Physik, Universit\"at 
  	Regensburg, 93040 Regensburg, Germany}
\affiliation[g]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
	% Auf der Morgenstelle 14, 
	D-72076 T\"ubingen, Germany}

@@

Resulting distributions $h^{\perp(1)q}_{1L}(x)$ are plotted in 
Fig.~\ref{g1t_h1l_functions}. 
The asymmetries $A_{UL}^{\sin(2\phi_h)}=F_{UL}^{\sin(2\phi_h)}/F_{UU}$  for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{aul_jlab}.

>>>>

\preprint{JLAB-THY-18-XXXX}

@@

\author[a]{S.~Bastami}
\author[c]{H.~Avakian}
\author[d]{A.~V.~Efremov} 
\author[e,f]{A.~Kotzinian} 
\author[g]{B.~U.~Musch} 
\author[e]{B.~Parsamyan} 
\author[b,c]{A.~Prokudin} 
\author[i]{M.~Schlegel} 
\author[]{G.~Schnell} 
\author[a,i]{P.~Schweitzer} 
\author[i]{W.~Vogelsang}

\affiliation[a]{Department of Physics, University of Connecticut, 
	Storrs, CT 06269, U.S.A.}
\affiliation[b]{Division of Science, Penn State Berks, Reading, 
	PA 19610, USA}
\affiliation[c]{Thomas Jefferson National Accelerator Facility, 
	Newport News, VA 23606, U.S.A.}
\affiliation[d]{Joint Institute for Nuclear Research, Dubna, 
	141980 Russia}
\affiliation[e]{Yerevan Physics Institute,
2 Alikhanyan Brothers St.,
375036 Yerevan, Armenia
}
\affiliation[f]{INFN, Sezione di Torino, 10125 Torino, Italy
}

\affiliation[g]{Institut f\"ur Theoretische Physik, Universit\"at 
  	Regensburg, 93040 Regensburg, Germany}
\affiliation[i]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
	% Auf der Morgenstelle 14, 
	D-72076 T\"ubingen, Germany}

@@

Resulting distributions $h^{\perp(1)q}_{1L}(x)$ are plotted in 
Fig.~\ref{g1t_h1l_functions}. 
The asymmetries $A_{UL}^{\sin(2\phi_h)}=F_{UL}^{\sin(2\phi_h)}/F_{UU}$  for 
 Jefferson Lab data from CLAS for neutral pion SIDIS \cite{Jawalkar:2017ube} are plotted in Fig.~\ref{aul_jlab}.
